---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crossfitgames

<!-- badges: start -->
<!-- badges: end -->

`{crossfitgames}` provides high-level functionality for retrieving data from the Crossfit Games API. It also provides some lower-level functionality for making requests to this API (if users prefer this level of access) as well as helper functions for accessing, reshaping, and cleaning data retrieved from the API.

It is loosely inspired by [Davis Vaughan's {crossfit} package](https://github.com/DavisVaughan/crossfit), which also provides functionality for accessing data from the Crossfit API.

## Installation

You can install the development version of crossfitgames from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ekholme/crossfitgames")
```

## Example

You might want to get final results from the Crossfit games in a given year. For example, you can get the data from the 2022 games for the women's division via the `games_leaderboard()` function.

```{r example}
library(crossfitgames)

women_22 <- games_leaderboard(2022, "women")
```

This will return a `cfg_leaderboard` R7 object. You can use methods associated with this object to extract more usable data:

```{r}
#will get the final leaderboard
final_lb <- extract_final_leaderboard(women_22)

head(final_lb)
```


```{r}
#will get event results for each athlete
event_results <- extract_workout_results(women_22)

head(event_results)
```