---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crossfitgames

<!-- badges: start -->
<!-- badges: end -->

`{crossfitgames}` provides high-level functionality for retrieving data from the Crossfit Games API. It also provides some lower-level functionality for making requests to this API (if users prefer this level of access) as well as helper functions for accessing, reshaping, and cleaning data retrieved from the API.

It is loosely inspired by [Davis Vaughan's {crossfit} package](https://github.com/DavisVaughan/crossfit), which also provides functionality for accessing data from the Crossfit API.

## Installation

You can install the development version of crossfitgames from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ekholme/crossfitgames")
```

## Example

*TODO*

```{r example}
library(crossfitgames)
## basic example code
```


