---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crossfitgames

<!-- badges: start -->
![GitHub last commit](https://img.shields.io/github/last-commit/ekholme/crossfitgames)
[![R-CMD-check](https://github.com/ekholme/crossfitgames/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ekholme/crossfitgames/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`{crossfitgames}` provides high-level functionality for retrieving data from the Crossfit Games API. It's still a work-in-progress, but the basic functionality is there to get data from the Games. I'll ge adding functionality to retrieve data from other competitions as well as functions to manipulate data from request results.

It is loosely inspired by [Davis Vaughan's {crossfit} package](https://github.com/DavisVaughan/crossfit), which also provides functionality for retrieving data from the Crossfit API.

## Installation

You can install the development version of crossfitgames from github with:

``` r
# install.packages("devtools")
devtools::install_github("ekholme/crossfitgames")
```

## Example

You might want to get final results from the Crossfit games in a given year. For example, you can get the data from the 2022 games for the women's division via the `games_leaderboard()` function.

```{r example}
library(crossfitgames)

women_22 <- games_leaderboard(2022, "women")
```

This will return a `cfg_leaderboard` S3 object. You can use methods associated with this object to extract more usable data:

```{r}
# will get the final leaderboard
final_lb <- extract_final_leaderboard(women_22)

head(final_lb)
```


```{r}
# will get event results for each athlete
event_results <- extract_workout_results(women_22)

head(event_results)
```
